Data- and Systems Paper: Identifying Handicap Parking Spots for Event's Venues

### 2016-04-09 milestone1/paper/paper.tex
added app screenshots [mls1]
added rdfs entailment figure [mls1]

\usepackage{url}
\usepackage{graphicx, colortbl}
\usepackage{amsmath,amssymb}	
\usepackage{listings}
\usepackage{multicol}
\usepackage{hyperref}
\lstset{language=SQL,morekeywords={PREFIX,java,rdf,rdfs,url}}

@@

The logical entailment rules are shown in the next argument:

@@

@@

\section{SQL Queries}

>>>>

\usepackage{url}
\usepackage{graphicx, colortbl}
\usepackage{amsmath,amssymb}	
\usepackage{listings}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{caption, subcaption}
\lstset{language=SQL,morekeywords={PREFIX,java,rdf,rdfs,url}}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{img/ontology-classes.png}
	\caption{RDFS entailment for our ontology. The Protege convention is adopted
	for symbols and colors: blue relations represent subclassing and yellow and
	orange ones represent domain and range relations.}
	\label{fig:rdfs-entailment}
\end{figure}

The logical entailment rules are shown in the next argument while a more
complete picture is shown in Figure \ref{rig:rdfs-entailment}:

@@

\begin{figure}
	\centering
	\begin{subfigure}[b]{.4\textwidth}
		\includegraphics[width=\textwidth]{img/app-venues.png}
		\caption{Venues shown by the Web application.}
		\label{fig:app-venues}
	\end{subfigure}
	\qquad
	\begin{subfigure}[b]{.4\textwidth}
		\includegraphics[width=\textwidth]{img/app-slots.png}
		\caption{Parking slots associated with a venue.}
		\label{fig:app-slots}
	\end{subfigure}
	\caption{Screenshots from the Web application.}
	\label{fig:app}
\end{figure}

@@

\section{SPARQL Queries}
